A Dearth of Young Stars and Planets in the Kepler Field

### 2024-06-05 paper/ms.tex
number fixing

Let us focus discussion on blemish-free stars with 
confirmed planets: $Q_{\rm star}$ must not have any of bits zero
through nine raised, and $Q_{\rm planet}$ must also have no quality flags
raised.  Under this constraint, our results include
\ltonegyrhighqconfirmedtwosided\ systems younger than 1\,Gyr with
two-sided $t_{\rm gyro}$ and $t_{\rm Li}$, and
\ltonegyrhighqconfirmedonesided\ cases for which $t_{\rm gyro}$
provides an age constraint while $t_{\rm Li}$ is one-sided.
%FIXME TODO GET MORE PRECISE LANGUAGE -- SYSTEMS OR PLANETS OR STARS?

These planets are shown in Figure~\ref{fig:rp_period_age_results}.
They include \nearthshighqconfirmed\ Earth-sized or smaller planets,
no Jupiter-sized or larger planets, \nsubsaturnshighqconfirmed\
``super-Neptune'' ($>$4\,$R_\oplus$) sized planets,
\nminineptuneshighqconfirmed\ mini-Neptunes above the radius valley
as parametrized by \citealt{2018MNRAS.479.4786V}, and
\nsuperearthshighqconfirmed\ super-Earth sized planets below the
radius valley.  While most of these planets are on orbital periods
below 50\,days, \nlongperiodhighqconfirmed\ are on more distant
orbits.

>>>>

Let us focus discussion on blemish-free stars with 
blemish-free planets: $Q_{\rm star}$ must not have any of bits zero
through nine raised, and $Q_{\rm planet}$ must similarly have no quality flags
raised.  Under this constraint, our results include
\ltonegyrhighqconfirmedtwosided\ confirmed planets younger than 1\,Gyr with
two-sided $t_{\rm gyro}$ and $t_{\rm Li}$, and
\ltonegyrhighqconfirmedonesided\ confirmed planets with comparable
ages for which $t_{\rm gyro}$
provides an age constraint while $t_{\rm Li}$ is one-sided.

Figure~\ref{fig:rp_period_age_results} shows
the planets and planet candidates with $t_{\rm gyro}$$<$1\,Gyr at
2$\sigma$.  
This figure includes \nconfirmedplyounggyrotwosigmanograzingnoruwe\
confirmed Kepler planets, and
\ncandidateplyounggyrotwosigmanograzingnoruwe\ candidate planets, all of which
are listed in Table~\ref{tab:planets}.
These include
\nearthshighqconfirmed\ Earth-sized or smaller planets,
one Jovian planet candidate, \nsubsaturnshighqconfirmed\
``super-Neptune'' ($>$4\,$R_\oplus$) sized planets,
\nminineptuneshighqconfirmed\ mini-Neptunes above the radius valley
as parametrized by \citealt{2018MNRAS.479.4786V}, and
\nsuperearthshighqconfirmed\ super-Earth sized planets below the
radius valley.  While most of these planets are on orbital periods
below 50\,days, \nlongperiodhighqconfirmed\ are on more distant
orbits.
